---
title: "Assignment 1 (Marketing Report)"
author: "Vaishnav Nayak"
format: 
  html:
    theme: cosmo
    toc: true
  pdf: 
    toc: true
---

```{r}
#| echo: false
#| message: false
#| warning: false
library(tidyverse)
library(ggplot2)
library(knitr)
library(kableExtra)
library(quarto)
library(lubridate)
```

## Introduction

To increase sales online marketplaces use personalized marketing. During the last quarter, our company ran a campaign where different customers spent different amounts. Determining whether higher spends lead to higher purchases is critical for future budget decisions. This report investigates the relationship between marketing spend and purchase amount from the campaign.

## Research Question

This report investigates whether higher marketing spend per customer leads to higher purchase amounts or not. Here we analyse the relationship between these two variables across all the customers in this dataset. Understanding this relationship will help us in future marketing budget decisions.

## Dataset Introduction

The dataset records marketing spend and purchase amounts for all individual customers during the campaign held in the last quarter. Every row represents a customer and some other details are included such as the signup date, purchase amount, customer segment,campaign notes, marketing spend and the number of website visits. The dataset was cleaned by removing rows with missing values. No other changes were necessary since the remaining variables were complete and correctly formatted.

```{r}
#| echo: false
#| message: false
#added the dataset
data <- read_csv("data/35546131_VaishnavNayak.csv") 


#cleaning the dataset
data <- data |>
  filter(notes != "N/A" | !is.na(purchase_amount)) |>
  drop_na(marketing_spend, purchase_amount) 
```

### Dataset Description

This dataset contains `r nrow(data)` observations and `r ncol(data)` variables, covering customer behaviour across different sectors.

```{r}
#| echo: false
#| tbl-cap: "Summary statistics (Average) by spend group and purchase power"

data |>
  group_by(segment) |>
  summarise(
    avg_spend = mean(marketing_spend),
    avg_purchase = mean(purchase_amount),
    n = n()
   ) |>
  kable(col.names = c("Segment", 
                      "Average Marketing Spend $", 
                      "Average Purchase Amount $", 
                      "Number of Customers"),
        digits = 2)
```

The table above summarizes the average marketing spend and purchase amount across each customer segment, giving us information on how spending was distributed throughout the campaign.

```{r}
#| echo: false
#| fig-cap: "Distribution of marketing spend across all customer segments"
#| label: fig-hist

#histogram
ggplot(data, aes(x = marketing_spend)) +
  geom_histogram(bins = 30, fill = "steelblue", color = "white") +
  labs(x = "Marketing Spend ($)", y = "Count") + 
  theme_minimal()
```

As shown in the @fig-hist, the marketing spend is spread across a wider range, indicating that the campaign deliberately varied investment levels across the customers.

## Results

```{r}
#| echo: false
#| results: hide
#| fig-cap: "Marketing spend vs Purchase amount"
#| label: fig-scatter
#| warning: false

#scatterplot
ggplot(data, aes(x = marketing_spend, y = purchase_amount)) +
  geom_point(alpha = 0.5, color = "red") +
  geom_smooth(method = "lm") +
  labs(x = "Marketing Spend ($)", y = "Purchase Amount ($)") +
  theme_minimal()
```

The @fig-scatter shows a positive relationship between marketing spend and purchase amount for all customers. The trend line (blue) suggests a positive associations, showcasing that the higher purchases were made by the customers on whom higher marketing spend was done.

```{r}
#| echo: false
#| results: hide
#| fig-cap: "Purchase amount by customer segment"
#| label: fig-box

#boxplot
ggplot(data, aes(x = segment, y = purchase_amount, fill = segment)) +
  geom_boxplot() +
  labs(x = "Customer Segment", y = "Purchase Amount ($)") +
  theme_minimal()
```

The @fig-box confirms that the amounts vary across customer segments, with some responding much better to the campaign than the others. Overall, the results suggest that higher marketing spend is associated with larger purchases, though the strength of the relationship may differ across the segments.
