---
title: "Assignment 1"
author: "Vaishnav Nayak"
format: html
  theme: cosmo
  toc: true
pdf:
  toc: true
---

##Loading the libraries\

```{r}
#| echo: false
#| message: false
#| warning: false
library(tidyverse)
library(ggplot2)
library(knitr)
library(kableExtra)
library(quarto)
library(lubridate)
```

##Introduction##

To increase sales online marketplaces use personalized marketing. Our company ran a campaign where different customers spent different amounts in the last quarter. Understanding whether higher spends lead to higher purchases is critical for future budget decisions. This report investigates the relationship using campaign data from Q3.

##Research Question##

This report investigates whether higher marketing spend per customer leads to higher purchase amounts. Here we analyse the relationship between these two variables across all customers in the Q3 campaign dataset.

##Dataset Introduction

The data records marketing spend and purchase amounts for individual customers during the Q3 campaign. The dataset was cleaned by removing rows with missing values and renaming columns for clarity.

```{r}
#| echo: false
#| message: false
#added the dataset
data <- read_csv("data/35546131_VaishnavNayak.csv") 


#cleaning the dataset
data <- data |>
  drop_na() |>
  rename(spend = marketing_spend,
         purchase = purchase_amount)
```

##Dataset Description

```{r}
#| echo: false
#| tbl-cap: "Summary statistics by spend group"

data |>
  group_by(spend) |>
  summarise(avg_purchase = mean(purchase)) |>
  kable()
```

```{r}
#| echo: false
#| fig-cap: "Distribution of marketing spend"
#| label: fig-hist

ggplot(data, aes(x = spend)) +
  geom_histogram(bins = 30) +
  labs(x = "Marketing spend", y = "Count") + 
  theme_minimal()
```

##Result

```{r}
#| echo: false
#| fig-cap: "Marketing spend vs Purchase amount"
#| label: fig-scatter
ggplot(data, aes(x = spend)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm") +
  labs(x = "Marketing spend", y = "Purchase amount") +
  theme_minimal()
```

```{r}
#| echo: false
#| fig-cap: "Purchase amount by spending group"
#| label: fig-box
ggplot(data, aes(x = spend)) +
  geom_boxplot()
  labs(x = "Spend group", y = "Purchase amount") +
  theme_minimal()
```

fig-scatter shows a positive relationship between spend and purchase amount. fig-box confirms that customers in higher spend groups tend to make larger purchases...
